### 2021-03-30 Chapter-3/Chapter-3.tex
Updates from Overleaf

CPUs can process data much faster than the main memory (DRAM) can supply it. To bridge the performance gap between the CPUs and the main memory, modern CPUs adopt a hierarchy memory. By storing extra copies of data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.

Figure~\ref{fig:memory_hierarchy} shows the overview of the hierarchy memory. For a CPU with multiple Cores, each core has two private level-1 (L1) cache, an instruction cache (iCache) and a data cache (dCache). Because instructions and data have different access patterns, separating iCache and dCache make it possible CPUs to fetch the code and data simultaneously and improve the performance. Followed by the level-1 cache, each core also has the unified private level-2 cache. The level-3 cache is the last level cache (LLC). The LLC is shared among all the cores. The main memory is the bottom-most under the memory hierarchy. 
\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter3/architecture.pdf}
    \caption{Computer Memory Hierarchy}\label{fig:memory_hierarchy}
\end{figure}

The current computer memory hierarchy opens the way for side-channel attacks from two aspects. First, the architecture relies on the system software to manage the addressing, which becomes a problem in a threat model where the operating system is not untrusted (e.g., Intel SGX). Second, the size of the cache is smaller than the main memory, which makes it possible that several program shares the same cache unit (e.g., cache line, cache set).

\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter3/address.pdf}
    \caption{Memory Addressing}\label{fig:memory_address}
\end{figure}

In modern CPUs, L1 and L2 caches are traditional N-way set associate caches. That is, the cache is divided into several cache sets, and each set is associated with several cache lines. The cache line is the atomic unit. As shown in Figure~\ref{fig:memory_address}, when the cache is accessed, the CPU uses the \textsf{Index} field of the address to locate a cache set. After that, it tries to use the \textsf{Tag} field to match every cache line inside the set line. If the CPU can locate a cache line with the same tag, then a cache hit occurs. The CPUs use a similar process to manage the main memory. The main memory is divided into many pages. As shown in Figure~\ref{fig:memory_address}, 
the translation process keeps the bottom bits while use the top bits to map the Physical Page Numbers to Virtual Page Numbers.

>>>>

CPUs process data in a much faster speed than the main memory (DRAM) can supply. Modern CPUs adopt a hierarchy memory to bridge the performance gap between the CPUs and the main memory. By storing extra copies of data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.

Figure~\ref{fig:memory_hierarchy} shows the overview of the hierarchy memory. For a CPU with multiple cores, each core has two private level-1 (L1) cache, an instruction cache (iCache), and a data cache (dCache). Because instructions and data have different access patterns, separating iCache and dCache makes it possible for CPUs to fetch the code and data and improve performance simultaneously. Followed by the level-1 cache, each core also has the unified private level-2 cache for both the code and the data. The level-3 cache is the last level cache (LLC). The LLC is shared among all the cores. The main memory is the bottom-most under the memory hierarchy. 
\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter3/architecture.pdf}
    \caption{Computer Memory Hierarchy}\label{fig:memory_hierarchy}
\end{figure}

The current computer memory hierarchy opens the way for side-channel attacks from two aspects. First, the architecture relies on the system software for managing the memory, which becomes a problem in a threat model where the operating system is not untrusted (e.g., Intel SGX). Second, the size of the cache is smaller than the main memory. Is is possible that different units in the main memory share the same address in the cache. 
\begin{figure}
    \centering
    \includegraphics[width=.65\columnwidth]{./figures/chapter3/address.pdf}
    \caption{Memory Addressing}\label{fig:memory_address}
\end{figure}

In modern CPUs, L1 and L2 caches are traditional N-way set associate caches. That is, the cache is divided into several cache sets, and each set is associated with several cache lines. The cache line is the atomic unit. As shown in Figure~\ref{fig:memory_address}, we can determine whether the data is in the cache with the folowing steps.  Given an address, the CPU uses the \textsf{Set Index} field of the address to locate the cache set that the address should reside in. After that, it tries to use the \textsf{Tag} field to match every cache line inside the set line. If the CPU can locate a cache line with the same tag and the valid bit is set, then a cache hit occurs. The CPUs use a similar process to manage the main memory. The main memory is divided into many units called pages. As shown in Figure~\ref{fig:memory_address}, 
the translation process keeps the bottom bits same while using the top bits to map the Physical Page Numbers to Virtual Page Numbers.
